---
title: "Untitled"
author: "RN7"
date: "June 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Recreate & Animate Your Favorite World Cup Goals!


## Gazinsky: First Goal!

```{r first goal}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(ggimage)
library(extrafont)
# loadfonts()

#                              2   1  
pass_data <- data.frame(x = c( 84, 82),
                        y = c(  6, 32),
                        x2 = c(77, 84),
                        y2 = c(13, 8))

#                            corner kick + golovin cross
curve_data <- data.frame(x = c(100, 76),
                         y = c(0, 19),
                         x2 = c(94, 94),
                         y2 = c(35, 60))

# Saudi failed clearance, Gazinsky header
ball_data <- data.frame(x = c(94, 94),
                        y = c(35, 60),
                        x2 = c(82, 99.2),
                        y2 = c(33.5, 47.5))

# soccer ball image
goal_img <- data.frame(x = 100,
                       y = 47) %>% 
  mutate(image = "https://d30y9cdsu7xlg0.cloudfront.net/png/43563-200.png")

# golovin + zhirkov movement
movement_data <- data.frame(x = c(83, 98),
                           y = c(24.25, 2),
                           x2 = c(77, 88),
                           y2 = c(21, 6))

g <- ggplot(pass_data) +
  annotate_pitch() +
  geom_segment(aes(x = x, y = y, xend = x2, yend = y2),
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_segment(data = ball_data,
               aes(x = x, y = y, xend = x2, yend = y2), 
               linetype = "dashed", size = 0.85,
               color = c("black", "red")) +
  geom_segment(data = movement_data,
               aes(x = x, y = y, xend = x2, yend = y2), 
               linetype = "dashed", size = 1.2,
               color = "darkgreen") +
  geom_curve(data = curve_data, 
             aes(x = x, y = y, xend = x2, yend = y2), 
             curvature = 0.25, 
             arrow = arrow(length = unit(0.25, "cm"),
                           type = "closed")) +
  geom_image(data = goal_img,
             aes(x = x, y = y,
                 image = image), 
             size = 0.035) +
  theme_pitch() + 
  theme(text = element_text(family = "Trebuchet MS")) +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  geom_label(aes(x = 94, y = 60, label = "Gazinsky"), hjust = -0.1) +
  geom_label(aes(x = 83, y = 23, label = "Golovin"), hjust = -0.05) +
  geom_label(aes(x = 75, y = 11, label = "Golovin"), hjust = -0.1) +
  geom_label(aes(x = 98, y = 0, label = "Zhirkov"), vjust = -0.3) +
  geom_label(aes(x = 84, y = 6, label = "Zhirkov"), vjust = -0.3) +
  annotate("text", x = 69, y = 65, family = "Trebuchet MS",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")

ggsave(g, filename = "gazinsky_goal.png")
```




## Cristiano Hat Trick

NOTE: you need to play around with the margins in `theme()` and the `width` or `height` arguments in `ggsave()` to remove the extraneous white space that appears.

```{r cristiano hat trick}
library(ggplot2)
library(ggsoccer)
library(extrafont)
library(emoGG)
library(ggimage)
# loadfonts()
# Official WC 2018 Font: "Dusha"
# http://fifa2018wiki.com/fifa-2018-font-typeface-download-dusha-font-ttf/509/

emoji_search("soccer")  # "26bd"

goals_data <- data.frame(x = c(88, 80, 71),
                         y = c(50, 48, 54),
                         label = c(1, 2, 3))

curve_data <- data.frame(x = c(88, 71), y = c(50, 54),
                         xend = c(100, 100), yend = c(54, 54))

annotation_data <- data.frame(
  hjust = c(0.5, 0.5, 0.5, 0, 0, 0),
  label = c("Portugal             (3) vs. Spain             (3)",
            "Cristiano's Hattrick (4', 44', 88')",
            "by Ryo Nakagawara (@R_by_Ryo)",
            "1. Fouled by Nacho in the box,\nCristiano confidently strokes the ball\ninto the right corner from the spot.",
            "2. Guedes lays it off to Cristiano whose\nstrong shot is uncharacteristically\nfumbled by De Gea into the net.",
            "In the final minutes of the game,\nCristiano wins a freekick against Pique\nand curls it beautifully over the wall."),
  x = c(110, 105, 53, 76, 66, 66), 
  y = c(30, 20, 85, 5, 5, 55)
)

flag_data <- data.frame(
  image = c("PT", "ES"),
  x = c(110, 110),
  y = c(19.1, 51.1)
)

# PLOT

cr <- ggplot(goals_data) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5"),
        legend.position = "none") +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_segment(x = 80, y = 48, 
               xend = 97, yend = 48) +  # 2nd 
  geom_segment(x = 97, y = 48, 
               xend = 100, yend = 45.5,
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +        # degea fumble
  geom_curve(data = curve_data,
             aes(x = x, y = y, 
                 xend = xend, yend = yend),     # FREEKICK
             curvature = 0.3, 
             arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
  geom_text(data = annotation_data,
            family = "Dusha V5", 
            aes(x = x, y = y,
                hjust = hjust, label = label),
            size = c(6.5, 4.5, 3, 3.5, 3.5, 3.5)) +
  geom_flag(data = flag_data,
            aes(x = x, y = y,
                image = image), size = c(0.08, 0.08)) +       # Portugal + Spain Flag
  ggimage::geom_emoji(aes(x = 105, 
                 y = c(45, 50, 55)),
             image = "26bd", size = 0.035) +
  geom_point(aes(x = x, y = y), 
             shape = 21, size = 7, color = "black", fill = "white") +
  geom_text(aes(x = x, y = y, label = label, family = "Dusha V5"))

ggsave(cr, filename = "cr_hattrick.png", height = 5)
```


## Osako's Winner against Colombia!


```{r osako winner}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(extrafont)
library(ggimage)


cornerkick_data <- data.frame(x = 99, y = 0.3,
                              x2 = 94, y2 = 47)

osako_gol <- data.frame(x = 94, y = 49,
                        x2 = 100, y2 = 55.5)

player_label <- data.frame(x = c(92, 99), 
                           y = c(49, 2))

wc_logo <- data.frame(x = 107,
                       y = 85) %>% 
  mutate(image = "https://upload.wikimedia.org/wikipedia/en/thumb/6/67/2018_FIFA_World_Cup.svg/1200px-2018_FIFA_World_Cup.svg.png")


g <- ggplot(osako_gol) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_curve(data = cornerkick_data,
             aes(x = x, y = y, xend = x2, yend = y2),
             curvature = -0.15, 
             arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_segment(aes(x = x, y = y, xend = x2, yend = y2),
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_label(data = player_label, 
             aes(x = x, y = y),
             label = c("Osako", "Honda"), family = "Dusha V5") +
  geom_point(aes(x = 98, y = 50), size = 3, color = "green") +
  geom_text(aes(x = 99.7, y = 50), size = 5, label = "???", family = "Dusha V5") +
  annotate(geom = "text", family = "Dusha V5", 
           hjust = c(0.5, 0.5, 0.5, 0.5, 0.5),
           size = c(6.5, 4.5, 4, 3.5, 3),
           label = c("Japan             (2) vs. Colombia             (1)",
                     "Kagawa (PEN 6'), Quintero (39'), Osako (73')",
                     "Japan press their man advantage, substitute Honda\ndelivers a delicious corner kick for Osako to (somehow) tower over\nColombia's defense and flick a header into the far corner!",
                     "Bonus: Ospina looking confused and\ndoing a lil' two-step-or-god-knows-what.",
                     "by Ryo Nakagawara (@R_by_Ryo)"),
           x = c(110, 105, 70, 92, 53), 
           y = c(30, 30, 45, 81, 85)) +
  ggimage::geom_flag(aes(image = "JP"),       # Japan Flag
            x = 110, y = 13, size = 0.08) +
  ggimage::geom_flag(aes(image = "CO"),       # Colombia Flag
            x = 110, y = 53, size = 0.08) +
  ggimage::geom_emoji(aes(x = 95, 
                          y = 50),
             image = "26bd", size = 0.035) +
  geom_image(data = wc_logo,
             aes(x = x, y = y,
                 image = image), size = 0.17) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
  
ggsave(g, filename = "osako_winner.png", height = 5)
```

## Animated version:

```{r osako anim}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(extrafont)
library(emoGG)
library(ggimage)
library(gganimate)


ball_data <- data.frame(x = c(99, 94, 100),
                        y = c(0.3, 47, 55.5),
                        time = c(1, 2, 3))

player_label <- data.frame(x = c(92, 97), 
                           y = c(48, 0))

wc_logo <- data.frame(x = 107,
                       y = 85) %>% 
  mutate(image = "https://upload.wikimedia.org/wikipedia/en/thumb/6/67/2018_FIFA_World_Cup.svg/1200px-2018_FIFA_World_Cup.svg.png")


g <- ggplot(ball_data) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_label(data = player_label, 
             aes(x = x, y = y),
             label = c("Osako", "Honda"), family = "Dusha V5") +
  geom_point(aes(x = 98, y = 50), size = 3, color = "green") +
  geom_text(aes(x = 99.7, y = 50), size = 5, label = "???", family = "Dusha V5") +
  annotate(geom = "text", family = "Dusha V5", 
           hjust = c(0.5, 0.5, 0.5, 0.5, 0.5),
           size = c(6.5, 4.5, 4, 3.5, 3),
           label = c("Japan             (2) vs. Colombia             (1)",
                     "Kagawa (PEN 6'), Quintero (39'), Osako (73')",
                     "Japan press their man advantage, substitute Honda\ndelivers a delicious corner kick for Osako to (somehow) tower over\nColombia's defense and flick a header into the far corner!",
                     "Bonus: Ospina looking confused and\ndoing a lil' two-step-or-god-knows-what.",
                     "by Ryo Nakagawara (@R_by_Ryo)"),
           x = c(110, 105, 70, 92, 53), 
           y = c(30, 30, 45, 81, 85)) +
  ggimage::geom_flag(aes(image = "JP"),       # Japan Flag
            x = 110, y = 13, size = 0.08) +
  ggimage::geom_flag(aes(image = "CO"),       # Colombia Flag
            x = 110, y = 53, size = 0.08) +
  ggimage::geom_emoji(aes(x = x, 
                          y = y,
                          frame = time),
             image = "26bd", size = 0.035) +
  geom_image(data = wc_logo,
             aes(x = x, y = y,
                 image = image), size = 0.17) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

g

gganimate(g, "osako_ani.gif") 

```

```{r osako tween}
# TWEEN

library(purrr)
library(tweenr)


ball_data <- data.frame(x = c(99, 94, 100),
                        y = c(0.3, 47, 55.5))

ball_list <- map(seq(nrow(ball_data)),
                      ~ ball_data[c(seq(.x), rep(.x, nrow(ball_data) - .x)), ])
  
osako_tween <- ball_list %>% 
  tween_states(tweenlength = 1.5, statelength = 0.1, ease = "linear", nframes = 50)

os_t <- osako_tween %>% group_by(.frame) %>% slice(3)
# take only changed 3rd value (1 and 2 of each frame are just copies of ball point origin coords)

ball_data <- data.frame(x = c(99, 94, 100),
                        y = c(0.3, 47, 55.5),
                        time = c(1, 2, 3))


ball_data <- ball_data %>% 
  mutate(group = rep(1:50, 1),
         ease = rep("linear", 3))

osako_tween2 <- tween_elements(ball_data, "time", "group", "ease",
                               nframes = 150)

g2 <- ggplot(os_t) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_label(data = player_label, 
             aes(x = x, y = y),
             label = c("Osako", "Honda"), family = "Dusha V5") +
  geom_point(aes(x = 98, y = 50), size = 3, color = "green") +
  annotate(geom = "text", family = "Dusha V5", 
           hjust = c(0.5, 0.5, 0.5, 0.5, 0.5),
           size = c(6.5, 4.5, 4, 3.5, 3),
           label = c("Japan             (2) vs. Colombia             (1)",
                     "Kagawa (PEN 6'), Quintero (39'), Osako (73')",
                     "Japan press their man advantage, substitute Honda\ndelivers a delicious corner kick for Osako to (somehow) tower over\nColombia's defense and flick a header into the far corner!",
                     "Bonus: Ospina looking confused and\ndoing a lil' two-step-or-god-knows-what.",
                     "by Ryo Nakagawara (@R_by_Ryo)"),
           x = c(110, 105, 70, 92, 53), 
           y = c(30, 30, 45, 81, 85)) +
  ggimage::geom_emoji(aes(x = x, 
                          y = y,
                          frame = .frame),
             image = "26bd", size = 0.035) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

g2

gganimate(g2, 
          ani.width = 800, ani.height = 500, 
          interval = 0.5,
          "osako_tween.gif") 

gganimate(g2, 
          ani.width = 800, ani.height = 500, 
          interval = 0.5,
          "osako_222.gif") 

# multiple balls appearing after every pause...?????? >>> fixed see above ost_t!
# fix how create list of df and tween_elements() >>> so original 2 points DONT show for each frame.

```



## Animate!

### Gazinsky animate

```{r Gazinsky ani data}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(ggimage)
library(extrafont)
library(gganimate)
library(tweenr)
# loadfonts()

# data
pass_data <- data.frame(
  x = c(100, 94, 82, 82.5,  84, 76.5, 75.5, 94, 99.2),       # pass balls
  y = c(0,   35, 31, 22,     8, 13, 19, 60, 47.5),
  label = "ball movement",
  time = c(1, 2, 3, 4, 5, 6, 7, 8, 9))

golovin_movement <- data.frame(
  x = c(78, 80, 80, 80, 75, 74, 73, 73, 73),
  y = c(30, 30, 27, 25,  10, 9, 15, 15, 15),
  label = "Golovin",
  time = c(1, 2, 3,  4,  5,  6,  7,  8,  9)
)

zhirkov_movement <- data.frame(
  x = c(98, 90, 84, 84, 84, 84, 84, 84, 84),
  y = c( 0,  2,  2,  2,  2,  2,  2,  2,  2),
  label = "Zhirkov",
  time = c(1, 2, 3, 4, 5, 6, 7, 8, 9)
)

gazinsky_movement <- data.frame(
  x = c(91.5),
  y = c(69),
  label = "Gazinsky",
  time = c(6, 7, 8, 9)
)

# segment golovin should only appear 4-5
# segment zhirkov should only appear 1-3
segment_data <- data.frame(
  x = c(77.5, 98),
  y = c(22, 2),
  xend = c(75, 84),
  yend = c(15, 3),
  linetype = c("dashed", "dashed"),
  color = c("darkgreen", "darkgreen"),
  size = c(1.2, 1.25)
)

saudi_data <- data.frame(
  x = c(95),
  y = c(35)
)

data <- tribble(
  ~x,  ~y,  ~label, ~time,
  100,  0,  "ball",     1,
   98,  0, "Golovin",   1,
   98,  0, "Zhirkov",   1,
   94, 35, "ball",      2,
   80, 30, "Golovin",   2,
   90,  2, "Zhirkov",   2,
   82, 31, "ball",      3,
   80, 25, "Golovin",   3,
   82,  3, "Zhirkov",   3, 
   82.5, 25, "ball",    4,
   80, 20, "Golovin",   4, 
   82,  3, "Zhirkov",   4,
   84,  6, "ball",      5, 
   75, 10, "Golovin",   5,
   82,  3, "Zhirkov",   5, 
   77, 13, "ball",      6,
   74,  9, "Golovin",   6,
   82,  3, "Zhirkov",   6,
   76, 19, "ball",      7,
   73, 15, "Golovin",   7,
   82,  3, "Zhirkov",   7,
   94, 60, "ball",      8,
   73, 20, "Golovin",   8,
   82,  3, "Zhirkov",   8,
   99.2, 47.5, "ball",  9,
   73, 20, "Golovin",   9,
   82,  3, "Zhirkov",   9
  
)
# arrange by time!
# instead of string label, give numerical ID value? but the IDs themselves will get "interpolated".... wtf

data2 <- data %>% select(-label)

```


```{r Gazinsky ani plot}
ani <- ggplot(pass_data) +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_label(
    data = golovin_movement,
    aes(x = x, y = y,
        frame = time,
        label = label)) +
  geom_label(
    data = zhirkov_movement,
    aes(x = x, y = y,
        frame = time,
        label = label)) +
  geom_label(
    data = gazinsky_movement,
    aes(x = x, y = y,
        frame = time,
        label = label)) +
  geom_point(
    data = saudi_data,
    aes(x = x, y = y),
    color = "darkgreen",
    size = 5) +
  ggimage::geom_emoji(
    aes(x = x, y = y, 
        frame = time), 
    image = "26bd", 
    size = 0.035) +
  theme(text = element_text(family = "Dusha V5")) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  annotate("text", x = 69, y = 65, family = "Dusha V5",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")

gganimate(ani, "ani.gif")  # use frame to check positionings...

```

A bit choppy, but the ball is in motion!

Let's fix this choppiness by interpolating our x,y coordinates to create a smoother animation between the passing points. 

Now use tweenr!

```{r Gazinsky tween data}
library(purrr)

# all tween
data_list <- map(seq(nrow(data)),
                      ~ data[c(seq(.x), rep(.x, nrow(data) - .x)), ])
  
data_tween <- data_list %>% 
  tween_states(tweenlength = 2, statelength = 1.25, ease = "linear", nframes = 200)    # Error in col2rgb(d) : invalid color name 'ball'


# sans labels col
data_list <- map(seq(nrow(data2)),
                      ~ data2[c(seq(.x), rep(.x, nrow(data2) - .x)), ])
  
data_tween <- data_list %>% 
  tween_states(tweenlength = 2, statelength = 1.25, ease = "linear", nframes = 200)


# plot

gazinsky_goal <- data_tween %>% 
  ggplot() +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_point(
    data = saudi_data,
    aes(x = x, y = y),
    color = "darkgreen",
    size = 5) +
  ggimage::geom_emoji(
    aes(x = x, y = y, frame = .frame),    # change frame to .frame or it'll still move by time only -_-
    image = "26bd", size = 0.035) +
  theme(text = element_text(family = "Dusha V5")) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  annotate("text", x = 69, y = 65, family = "Dusha V5",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")
  
  

# you can seee the ball "travelling along"

gganimate(gazinsky_goal, 
          ani.width = 800, ani.height = 500, 
          interval = 0.25, 
          "gazinsky_goal.gif")

```

- try with tween_elements() again........

```{r Gazinsky movement tweenr}
golovin_movement_list <- map(seq(nrow(golovin_movement)),
                      ~golovin_movement[c(seq(.x), rep(.x, nrow(golovin_movement) - .x)), ])
  
golovin_tween <- golovin_movement_list %>% 
  tween_states(tweenlength = 2, statelength = 1.5, ease = "linear", nframes = 200)

gazinsky_goal <- ggplot(pass_data) +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_label(
    aes(x = x2, y = y2,
        frame = time,
        label = label)) +
  ggimage::geom_emoji(
    aes(x = x, y = y, frame = time), 
    image = "26bd", size = 0.035)

gganimate(gazinsky_goal, 
          ani.width = 800, ani.height = 500, 
          title_frame = FALSE, interval = 0.25, 
          "gazinsky_goal.gif")
```

PR for formations function?

Try more advanced soccer play-by-play animations?

Recreate famous World Cup goals of the past? (Maradona vs. England?)


## Japan's Offside Trap!

```{r}

```

+ the meme generator with R

```{r meme}
library(memery)
img <- ("https://imgflip.com/s/meme/Roll-Safe-Think-About-It.jpg")

meme_labs <- c("you can't lose the aerial battle", "if you set an offside trap")

meme(img, meme_labs, "offside_meme.png")

```

