---
title: "Untitled"
author: "RN7"
date: "June 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Recreate & Animate Your Favorite World Cup Goals!



Let's look at some of the packages we will use!

```{r}

```

You can also grab images from URLs and 


```{r}

```







First Goal!

```{r first goal}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(ggimage)
library(extrafont)
# loadfonts()

#                              2   1  
pass_data <- data.frame(x = c( 84, 82),
                        y = c(  6, 32),
                        x2 = c(77, 84),
                        y2 = c(13, 8))

#                            corner kick + golovin cross
curve_data <- data.frame(x = c(100, 76),
                         y = c(0, 19),
                         x2 = c(94, 94),
                         y2 = c(35, 60))

# Saudi failed clearance 
clearance_data <- data.frame(x = c(94),
                             y = c(35),
                             x2 = c(82),
                             y2 = c(33.5))

# Gazinski header
goal_data <- data.frame(x = c(94),
                        y = c(60),
                        x2 = c(99.2),
                        y2 = c(47.5))

# soccer ball image
goal_img <- data.frame(x = 100,
                       y = 47) %>% 
  mutate(image = "https://d30y9cdsu7xlg0.cloudfront.net/png/43563-200.png")

# golovin movement
golovin_data <- data.frame(x = c(83),
                           y = c(24.25),
                           x2 = c(77),
                           y2 = c(21))

# zhirkov movement 
zhirkov_data <- data.frame(x = 98,
                           y = 2,
                           x2 = 88,
                           y2 = 6)

g <- ggplot(pass_data) +
  annotate_pitch() +
  geom_segment(aes(x = x, y = y, xend = x2, yend = y2),
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_segment(data = clearance_data,
               aes(x = x, y = y, xend = x2, yend = y2
                   ), linetype = "dashed", size = 0.85) +
  geom_segment(data = goal_data,
               aes(x = x, y = y, xend = x2, yend = y2
                   ), linetype = "dashed", color = "red", size = 0.85) +
  geom_segment(data = golovin_data,
               aes(x = x, y = y, xend = x2, yend = y2
                   ), linetype = "dashed", color = "darkgreen", size = 1.2) +
  geom_segment(data = zhirkov_data,
               aes(x = x, y = y, xend = x2, yend = y2
                   ), linetype = "dashed", color = "darkgreen", size = 1.25) +
  geom_curve(data = curve_data, 
             aes(x = x, y = y, xend = x2, yend = y2), 
             curvature = 0.25, 
             arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_image(data = goal_img,
             aes(x = x, y = y,
                 image = image), size = 0.035) +
  theme_pitch() + 
  theme(text = element_text(family = "Trebuchet MS")) +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  geom_label(aes(x = 94, y = 60, label = "Gazinsky"), hjust = -0.1) +
  geom_label(aes(x = 83, y = 23, label = "Golovin"), hjust = -0.05) +
  geom_label(aes(x = 75, y = 11, label = "Golovin"), hjust = -0.1) +
  geom_label(aes(x = 98, y = 0, label = "Zhirkov"), vjust = -0.3) +
  geom_label(aes(x = 84, y = 6, label = "Zhirkov"), vjust = -0.3) +
  annotate("text", x = 69, y = 65, family = "Trebuchet MS",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")

ggsave(g, filename = "gazinsky_goal.png")
```



Cristiano Hat Trick

NOTE: you need to play around with the margins in `theme()` and the `width` or `height` arguments in `ggsave()` to remove the extraneous white space that appears.

```{r cristiano hat trick}
library(ggplot2)
library(ggsoccer)
library(extrafont)
library(emoGG)
library(ggimage)
# loadfonts()
# Official WC 2018 Font: "Dusha"
# http://fifa2018wiki.com/fifa-2018-font-typeface-download-dusha-font-ttf/509/

emoji_search("soccer")  # "26bd"

goals_data <- data.frame(x = c(88, 80, 71),
                         y = c(50, 48, 54))

curve_data <- data.frame(x = c(88, 71), y = c(50, 54),
                         xend = c(100, 100), yend = c(54, 54))

annotation_data <- data.frame(
  hjust = c(0.5, 0.5, 0.5, 0, 0, 0),
           size = c(6.5, 4.5, 3, 3.5, 3.5, 3.5),
           label = c("Portugal             (3) vs. Spain             (3)",
                     "Cristiano's Hattrick (4', 44', 88')",
                     "by Ryo Nakagawara (@R_by_Ryo)",
                     "1. Fouled by Nacho in the box,\nCristiano confidently strokes the ball\ninto the right corner from the spot.",
                     "2. Guedes lays it off to Cristiano whose\nstrong shot is uncharacteristically\nfumbled by De Gea into the net.",
                     "In the final minutes of the game,\nCristiano wins a freekick against Pique\nand curls it beautifully over the wall."),
           x = c(110, 105, 53, 76, 66, 66), 
           y = c(30, 20, 85, 5, 5, 55)
)

flag_data <- data.frame(
  image = c("PT, ES"),
  x = c(110, 110),
  y = c(19.1, 51.1),
  size = 0.08
)

# PLOT

cr <- ggplot(goals_data) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_segment(x = 80, y = 48, 
               xend = 97, yend = 48) +  # 2nd 
  geom_segment(x = 97, y = 48, 
               xend = 100, yend = 45.5,
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +        # degea fumble
  geom_curve(data = curve_data,
             aes(x = x, y = y, 
                 xend = xend, yend = yend),     # FREEKICK
             curvature = 0.3, 
             arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
  geom_text(data = annotation_data,
            family = "Dusha V5", 
            aes(x = x, y = y,
                hjust = hjust, size = size, label = label)) +
  ggimage::geom_flag(data = flag_data,
                     aes(x = x, y = y,
                       image = image, size = size)       # Portugal Flag
                     ) +
  ggimage::geom_emoji(aes(x = 105, 
                          y = c(45, 50, 55)),
             image = "26bd", size = 0.035) +
  geom_point(aes(x = x, y = y), 
             shape = 21, size = 7, color = "black", fill = "white") +
  geom_text(aes(x = x, y = y, label = c(1, 2, 3)), family = "Dusha V5")

ggsave(cr, filename = "cr_hattrick.png", height = 5)
```


```{r check flags}

goals_data <- data.frame(x = c(88, 80, 71),
                         y = c(50, 48, 54))

flag_data <- data.frame(
  image = c("PT, ES"),
  x = c(110, 110),
  y = c(19.1, 51.1),
  size = 0.08
)


ggplot(goals_data) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  ggimage::geom_flag(data = flag_data,
                     aes(x = x, y = y,
                       image = image, size = size)) 
```




Osako's Winner against Colombia!


```{r osako winner}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(extrafont)
library(emoGG)
library(ggimage)


cornerkick_data <- data.frame(x = 99, y = 0.3,
                              x2 = 94, y2 = 47)

osako_gol <- data.frame(x = 94, y = 49,
                        x2 = 100, y2 = 55.5)

player_label <- data.frame(x = c(92, 99), 
                           y = c(49, 2))

wc_logo <- data.frame(x = 107,
                       y = 85) %>% 
  mutate(image = "https://upload.wikimedia.org/wikipedia/en/thumb/6/67/2018_FIFA_World_Cup.svg/1200px-2018_FIFA_World_Cup.svg.png")


g <- ggplot(osako_gol) +
  annotate_pitch() +
  theme_pitch() +
  theme(text = element_text(family = "Dusha V5")) +
  coord_flip(xlim = c(55, 112),
             ylim = c(-1, 101)) +
  geom_curve(data = cornerkick_data,
             aes(x = x, y = y, xend = x2, yend = y2),
             curvature = -0.15, 
             arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_segment(aes(x = x, y = y, xend = x2, yend = y2),
               arrow = arrow(length = unit(0.25, "cm"),
                             type = "closed")) +
  geom_label(data = player_label, 
             aes(x = x, y = y),
             label = c("Osako", "Honda"), family = "Dusha V5") +
  geom_point(aes(x = 98, y = 50), size = 3, color = "green") +
  geom_text(aes(x = 99.7, y = 50), size = 5, label = "???", family = "Dusha V5") +
  annotate(geom = "text", family = "Dusha V5", 
           hjust = c(0.5, 0.5, 0.5, 0.5, 0.5),
           size = c(6.5, 4.5, 4, 3.5, 3),
           label = c("Japan             (2) vs. Colombia             (1)",
                     "Kagawa (PEN 6'), Quintero (39'), Osako (73')",
                     "Japan press their man advantage, substitute Honda\ndelivers a delicious corner kick for Osako to (somehow) tower over\nColombia's defense and flick a header into the far corner!",
                     "Bonus: Ospina looking confused and\ndoing a lil' two-step-or-god-knows-what.",
                     "by Ryo Nakagawara (@R_by_Ryo)"),
           x = c(110, 105, 70, 92, 53), 
           y = c(30, 30, 45, 81, 85)) +
  ggimage::geom_flag(aes(image = "JP"),       # Japan Flag
            x = 110, y = 13, size = 0.08) +
  ggimage::geom_flag(aes(image = "CO"),       # Colombia Flag
            x = 110, y = 53, size = 0.08) +
  ggimage::geom_emoji(aes(x = 95, 
                          y = 50),
             image = "26bd", size = 0.035) +
  geom_image(data = wc_logo,
             aes(x = x, y = y,
                 image = image), size = 0.17) +
  theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
  
ggsave(g, filename = "osako_winner.png", height = 5)
```



VAR Decisions

```{r var }

```




Shots on Goal: On + Off Target

```{r shots on goal}

```


## Formation and line-ups

make function for set formations 
- all you need to do is pass player names and formation string ("3-5-2", "4-4-2", etc.)
- later version: player icon with uniform (like in Wikipedia)

```{r formations}

```



### Animate!


```{r animate}
library(ggplot2)
library(dplyr)
library(ggsoccer)
library(ggimage)
library(extrafont)
library(gganimate)
library(tweenr)
# loadfonts()

# data
pass_data <- data.frame(
  x = c(100, 94, 82, 82.5,  84, 77, 76, 94, 99.2),# pass balls
  y = c(0,   35, 31, 25,  6, 13, 19, 60, 47.5),
  x2 = c(78, 78, 78, 73, 73, 73, 73, 73, 73),     # golovin movement
  y2 = c(26, 25, 23, 9, 9, 9, 9, 9, 9),
  label = "Golovin",
  time = c(1, 2, 3, 4, 5, 6, 7, 8, 9))

label_data <- data.frame(
  x = c(94, 78, 73, 98, 82),
  y = c(60, 26, 9, 0, 3),
  time = c(1, 2, 3, 1, 3),
  label = c("Gazinsky", "Golovin", "Golovin", "Zhirkov", "Zhirkov"),
  hjust = c(-0.1, -0.05, -0.1, 0, 0),
  vjust = c(0, 0, 0, -0.3, -0.3)
)


  geom_label(
    data = label_data,
    aes(x = x, y = y, 
        frame = time,
        label = label, 
        hjust = hjust, vjust = vjust)) 


golovin_movement <- data.frame(
  x = c(78, 78, 78, 73, 73, 73, 73, 73, 73),
  y = c(26, 25, 23, 9, 9, 9, 9, 9, 9),
  label = "Golovin",
  time = c(1, 2, 3, 4, 5, 6, 7, 8, 9)
)

# 1. gazinsky header, 2. golovin movement, 3. zhirkov movement:
segment_data <- data.frame(
  x = c(83, 98),
  y = c(24.25, 2),
  xend = c(77, 88),
  yend = c(21, 6),
  linetype = c("dashed", "dashed"),
  color = c("darkgreen", "darkgreen"),
  size = c(1.2, 1.25)
)

saudi_data <- data.frame(
  x = c(95),
  y = c(35)
)

ani <- ggplot(pass_data) +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_label(
    data = golovin_movement,
    aes(x = x, y = y,
        frame = time,
        label = label)) +
#+
  geom_point(
    data = saudi_data,
    aes(x = x, y = y),
    color = "darkgreen",
    size = 5) +
  ggimage::geom_emoji(
    aes(x = x, y = y, 
        frame = time), 
    image = "26bd", 
    size = 0.035) +
  theme(text = element_text(family = "Dusha V5")) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  annotate("text", x = 69, y = 65, family = "Dusha V5",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")

gganimate(ani, "ani.gif", title_frame = FALSE)

```

A bit choppy, but the ball is in motion!

Let's fix this choppiness by interpolating our x,y coordinates to create a smoother animation between the passing points. 




Now use tweenr!

```{r}
library(purrr)

pass_data_list <- map(seq(nrow(pass_data)),
                      ~pass_data[c(seq(.x), rep(.x, nrow(pass_data) - .x)), ])
  
pass_tween <- pass_data_list %>% 
  tween_states(tweenlength = 2, statelength = 1.5, ease = "linear", nframes = 200)

gazinsky_goal <- pass_tween %>% 
  ggplot() +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_label(
    data = label_data,
    aes(x = x, y = y, 
        label = label, 
        hjust = hjust, vjust = vjust)) +
  geom_point(
    data = saudi_data,
    aes(x = x, y = y),
    color = "darkgreen",
    size = 5) +
  ggimage::geom_emoji(
    aes(x = x, y = y, frame = time), 
    image = "26bd", size = 0.035) +
  theme(text = element_text(family = "Dusha V5")) +
  ggtitle(label = "Russia (5) vs. (0) Saudi Arabia", 
          subtitle = "First goal, Yuri Gazinsky (12th Minute)") +
  labs(caption = "By Ryo Nakagawara (@R_by_Ryo)") +
  annotate("text", x = 69, y = 65, family = "Dusha V5",
           label = "After a poor corner kick clearance\n from Saudi Arabia, Golovin picks up the loose ball, \n exchanges a give-and-go pass with Zhirkov\n before finding Gazinsky with a beautiful cross!")
  
  

# you can seee the ball "travelling along"

gganimate(gazinsky_goal, 
          ani.width = 800, ani.height = 500, 
          title_frame = FALSE, interval = 0.25, 
          "gazinsky_goal.gif")

```


- shift coordinates to make ball look like being dribbled by the player labels
- track player runs? necessary? maybe just as extra step.
- add Saudi player clearance as Green Dot
- try with tween_elements() again........



```{r}
golovin_movement_list <- map(seq(nrow(golovin_movement)),
                      ~golovin_movement[c(seq(.x), rep(.x, nrow(golovin_movement) - .x)), ])
  
golovin_tween <- golovin_movement_list %>% 
  tween_states(tweenlength = 2, statelength = 1.5, ease = "linear", nframes = 200)




gazinsky_goal <- ggplot(pass_data) +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101)) +
  geom_segment(data = segment_data, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend),
               size = segment_data$size,
               color = segment_data$color,
               linetype = c("dashed", "dashed")) +
  geom_label(
    aes(x = x2, y = y2,
        frame = time,
        label = label)) +
  ggimage::geom_emoji(
    aes(x = x, y = y, frame = time), 
    image = "26bd", size = 0.035)

gganimate(gazinsky_goal, 
          ani.width = 800, ani.height = 500, 
          title_frame = FALSE, interval = 0.25, 
          "gazinsky_goal.gif")
```



PR for formations function?

Try more advanced soccer play-by-play animations?

Recreate famous World Cup goals of the past? (Maradona vs. England?)



```{r}
pass_data <- data.frame(x = c(100, 94, 82,  84, 77, 76, 94, 99.2),
                        y = c(0,   35, 33.5, 6, 13, 19, 60, 47.5),
                        time = c(1, 2, 3, 4, 5, 6, 7, 8))

data <- data.frame(x = 1, y = 1)

ggplot(data) +
  annotate_pitch() +
  theme_pitch() +
  coord_flip(xlim = c(49, 101),
             ylim = c(-1, 101))
```




