---
title: "final matchday group"
author: "RN7"
date: "June 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Group A Standings throughout Final Matchday!

```{r fig.width=7, fig.height=6}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
# loadfonts()  run once per new session!

group_a <- data.frame(

  time = c(1, 2, 3, 4),
  russia = c(1, 2, 2, 2),
  uruguay = c(2, 1, 1, 1),
  egypt = c(3, 3, 4, 4),
  saudi_arabia = c(4, 4, 3, 3)
  
)

group_a <- group_a %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = recode_factor(team, "saudi_arabia" = "saudi arabia")) %>% 
  mutate(team = fct_relevel(team, 
                            "russia", "uruguay", "egypt", "saudi arabia"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "10'", "90 + 5'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 4, 4, 4),
  y = c(1, 3, 1, 2, 3, 4),
  score = c("1-0", "2-1", "3-0", "0-3", "2-1", "1-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Russia", "Uruguay", "Egypt", "Saudi Arabia")
)

goals_labs <- data.frame(
  x = c(4, 4, 4),
  y = c(1, 3, 4),
  scorers = c("Suarez (10')\nCheryshev o.g. (23')\nCavani (90')",
              "Al-Faraj pen. (45+6')\nAl-Dawsari (90+5')",
              "Salah (22')")
)


## plot

groupA <- ggplot(
  group_a,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.1) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.25, size = 7) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.25, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.3, size = 3) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.5, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:4,
    labels = x_labs,
    limits = c(0.5, 4.5)) +
  labs(
    x = "", y = "",
    title = "Group A Table Throughout The Last Matchday",
    subtitle = "Uruguay vs. Russia & Saudi Arabia vs. Egypt",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupA, filename = "groupA_table.png")
```




## Group B Standings during Final Match Day!

```{r fig.width=10, fig.height=6}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
# loadfonts()  run once per new session!

group_b <- data.frame(

  time = c(1, 2, 3, 4, 5, 6, 7, 8),
  spain = c(1, 2, 1, 2, 2, 2, 1, 1),
  portugal = c(2, 1, 2, 1, 1, 1, 2, 2),
  iran = c(3, 3, 3, 3, 4, 3, 3, 3),
  morocco = c(4, 4, 4, 4, 3, 4, 4, 4)
  
)

group_b <- group_b %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "spain", "portugal", "iran", "morocco"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "14'", "19'", "45'", "81'", "90 + 1'", "90 + 3'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 5, 6, 7, 8, 8, 8, 8),
  y = c(2, 1, 1, 3, 4, 2, 1, 2, 3, 4),
  score = c("0-1", "1-1", "1-0", "2-1", "2-2", "1-1",
            "2-2", "1-1", "1-1", "2-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Spain", "Portugal", "Iran", "Morocco")
)

goals_labs <- data.frame(
  x = c(8, 8, 8, 8),
  y = c(1, 2, 3, 4),
  scorers = c("Isco (19')\nAspas (90+1')",
              "Quaresma (45')",
              "Ansarifard pen. (90+3')",
              "Boutaib (14')\nEn-Nesyri (81')")
)

## PLOT

groupB <- ggplot(
  group_b,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.1) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.25, size = 7) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.25, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.25, size = 3) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.5, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:8,
    labels = x_labs,
    limits = c(0.5, 8.5)) +
  labs(
    x = "", y = "",
    title = "Group B Table Throughout The Last Matchday",
    subtitle = "Iran vs. Portugal & Spain vs. Morocco",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupB, filename = "groupB_table.png")
```

how to emphasize IRAN vs. PORTUGAL and SPAIN sv. MOROCCO   ???

place scorer name below flags?


## Group C Standings During Final Matchday!

```{r fig.width=10, fig.height=6}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
# loadfonts()  run once per new session!

group_c <- data.frame(

  time =      c(1, 2, 3, 4),
  france =    c(1, 1, 1, 1),
  denmark =   c(2, 2, 2, 2),
  australia = c(3, 4, 4, 4),
  peru =      c(4, 3, 3, 3)
  
)

group_c <- group_c %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "france", "denmark", "australia", "peru"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "18'", "50'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 4, 4, 4),
  y = c(3, 3, 1, 2, 3, 4),
  score = c("1-0", "2-0", "0-0", "0-0", "2-0", "0-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("France", "Denmark", "Australia", "Peru")
)

goals_labs <- data.frame(
  x = c(2, 3),
  y = c(3, 3),
  scorers = c("Carillo (18')", "Guerrero (50')")
)

points_labs <- data.frame(
  x = c(4.5, 4.5, 4.5, 4.5),
  y = c(1, 2, 3, 4),
  points = c("7 pts.", "5 pts.", "3 pts.", "1 pts.")
)

## PLOT

groupC <- ggplot(
  group_c,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.11) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.3, size = 4) +
  geom_text(
    data = points_labs,
    aes(x = x, y = y, 
        label = points,
        family = "Dusha V5"),
    size = 5) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.5, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:4,
    labels = x_labs,
    expand = c(0, 0),
    limits = c(0.7, 4.7)) +
  labs(
    title = "Group C Table Throughout The Last Matchday",
    subtitle = "Denmark vs. France & Australia vs. Peru",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    axis.title = element_blank(),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupC, filename = "groupC_table.png")
```


## Group D Standings During Final Matchday!

NOTE: Argentina in 4th at start due to more yellow cards in tie-breaker vs. Iceland.

```{r fig.width=9, fig.height=5}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
# loadfonts()  run once per new session!

group_d <- data.frame(

  time =      c(1, 2, 3, 4, 5, 6, 7),
  croatia =   c(1, 1, 1, 1, 1, 1, 1),
  nigeria =   c(2, 3, 2, 2, 2, 3, 3),
  iceland =   c(3, 4, 3, 4, 3, 4, 4),
  argentina = c(4, 2, 4, 3, 4, 2, 2)
  
)

group_d <- group_d %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "croatia", "nigeria", "argentina", "iceland"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "14'", "51'", "53'", "76'", "86'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 5, 6, 7, 7, 7, 7),
  y = c(2, 2, 4, 3, 2, 1, 2, 3, 4),
  score = c("1-0", "1-1", "0-1", "1-1", "2-1", 
            "2-1", "2-1", "1-2", "1-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Croatia", "Nigeria", "Iceland", "Argentina")
)

goals_labs <- data.frame(
  x = c(2, 3, 4, 5, 6, 7),
  y = c(2, 2, 4, 3, 2, 1),
  scorers = c("Messi", "Moses (pen.)", "(Croatia)\nBadelj", 
              "G. Sigurdsson (pen.)", "Rojo", "Perisic (90')")
)

points_labs <- data.frame(
  x = c(7.8, 7.8, 7.8, 7.8),
  y = c(1, 2, 3, 4),
  points = c("9 pts.", "4 pts.", "3 pts.", "1 pts.")
)

## PLOT

groupD <- ggplot(
  group_d,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.11) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.38, size = 4) +
  geom_text(
    data = points_labs,
    aes(x = x, y = y, 
        label = points,
        family = "Dusha V5"),
    size = 5) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.8, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:7,
    labels = x_labs,
    expand = c(0, 0),
    limits = c(0.4, 8.3)) +
  labs(
    title = "Group D Table Throughout The Last Matchday",
    subtitle = "Nigeria vs. Argentina & Iceland vs. Croatia",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    axis.title = element_blank(),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupD, filename = "groupD_table.png")
```


## Group E Standings During Final Matchday!

```{r fig.width=8, fig.height=5}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
#loadfonts()  run once per new session!

group_e <- data.frame(

  time =        c(  1, 2, 3, 4),
  brazil =     c(   1, 2, 1, 1),
  switzerland = c(  2, 1, 2, 2),
  serbia =     c(   3, 3, 3, 3),
  costa_rica = c(   4, 4, 4, 4)
  
)

group_e <- group_e %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = recode_factor(team, "costa_rica" = "costa rica")) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "brazil", "switzerland", "serbia", "costa rica"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "31'", "36'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 4, 4, 4),
  y = c(1, 1, 1, 2, 3, 4),
  score = c("1-0", "1-0", "2-0", "2-2", 
            "0-2", "2-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Brazil", "Switzerland", "Serbia", "Costa Rica")
)

goals_labs <- data.frame(
  x = c(2, 3, 4, 4, 4),
  y = c(1, 1, 4, 1, 2),
  scorers = c("Dzemaili", "Paulinho", 
              "Waston (56')\nSommer o.g. (90+3')", "Thiago Silva (68')", "Drmic (88')")
)

points_labs <- data.frame(
  x = c(5.8, 5.8, 5.8, 5.8),
  y = c(1, 2, 3, 4),
  points = c("7 pts.", "5 pts.", "3 pts.", "1 pts.")
)

## PLOT

groupE <- ggplot(
  group_e,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.1) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.33, size = 6) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.35, size = 4) +
  geom_text(
    data = points_labs,
    aes(x = x, y = y, 
        label = points,
        family = "Dusha V5"),
    size = 5) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.8, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:4,
    labels = x_labs,
    expand = c(0, 0),
    limits = c(0.4, 5.3)) +
  labs(
    title = "Group E Table Throughout The Last Matchday",
    subtitle = "Serbia vs. Brazil & Switzerland vs. Costa Rica",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    axis.title = element_blank(),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupE, filename = "groupE_table.png")

```


## Group F Standings During Final Matchday!

```{r fig.width=8, fig.height=5}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
#loadfonts()  run once per new session!

group_f <- data.frame(

  time =      c(  1, 2, 3, 4, 5),
  mexico =   c(   1, 1, 2, 2, 2),
  germany =   c(  2, 3, 3, 4, 4),
  sweden =   c(   3, 2, 1, 1, 1),
  south_korea = c(4, 4, 4, 3, 3)
  
)

group_f <- group_f %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team),
         team = recode_factor(team, "south_korea" = "south korea")) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "mexico", "germany", "sweden", "south korea"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "50'", "60'", "90+3'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 5, 5, 5, 5),
  y = c(2, 1, 3, 1, 2, 3, 4),
  score = c("1-0", "2-0", "1-0", 
            "3-0", "0-3", "2-0", "0-2")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Mexico", "Germany", "Sweden", "South Korea")
)

goals_labs <- data.frame(
  x = c(2, 3, 4, 5, 5),
  y = c(2, 1, 3, 1, 3),
  scorers = c("Augustinsson", "Granqvist (pen.)", "Kim Y-G", 
              "Alvarez o.g. (74')", "Son H-M (90+6')")
)

points_labs <- data.frame(
  x = c(5.8, 5.8, 5.8, 5.8),
  y = c(1, 2, 3, 4),
  points = c("6 pts.", "6 pts.", "3 pts.", "3 pts.")
)

## PLOT

groupF <- ggplot(
  group_f,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.11) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.25, size = 4) +
  geom_text(
    data = points_labs,
    aes(x = x, y = y, 
        label = points,
        family = "Dusha V5"),
    size = 5) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.8, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:5,
    labels = x_labs,
    expand = c(0, 0),
    limits = c(0.4, 6.3)) +
  labs(
    title = "Group F Table Throughout The Last Matchday",
    subtitle = "South Korea vs. Germany & Mexico vs. Sweden",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    axis.title = element_blank(),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupF, filename = "groupF_table.png")
```




## Group H Standings During Final Matchday!



```{r fig.width=8, fig.height=5}
library(dplyr)
library(ggplot2)
library(ggimage)
library(countrycode)
library(tidyr)
library(forcats)
library(extrafont)
#loadfonts()  run once per new session!

group_h <- data.frame(

  time =      c( 1, 2, 3, 4),
  japan =   c(   1, 3, 2, 2),
  senegal =   c( 2, 2, 3, 3),
  colombia =   c(3, 1, 1, 1),
  poland = c(    4, 4, 4, 4)
  
)

group_h <- group_h %>% 
  gather(team, position, -time) %>% 
  mutate(team = as.factor(team)) %>% 
  mutate(team = as.factor(team),
         team = fct_relevel(team, 
                            "japan", "senegal", "colombia", "poland"),
         flag = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))

x_labs <- c("0'", "59'", "74'", "Full Time")
y_labs <- c("1st", "2nd", "3rd", "4th")

score_labs <- data.frame(
  x = c(2, 3, 4, 4, 4, 4),
  y = c(3, 1, 1, 2, 3, 4),
  score = c("0-1", "1-0", 
            "1-0", "0-1", "0-1", "1-0")
)

country_labs <- data.frame(
  x = c(1, 1, 1, 1),
  y = c(1, 2, 3, 4),
  country = c("Japan", "Senegal", "Colombia", "Poland")
)

goals_labs <- data.frame(
  x = c(2, 3),
  y = c(3, 1),
  scorers = c("Bednarek (Poland)", "Mina")
)

points_labs <- data.frame(
  x = c(4.8, 4.8, 4.8, 4.8),
  y = c(1, 2, 3, 4),
  points = c("6 pts.", "4 pts.", "4 pts.", "3 pts.")
)

## PLOT

groupH <- ggplot(
  group_h,
  aes(time, position)) +
  geom_line(
    aes(group = team), linetype = "dotted") +
  geom_flag(
    aes(image = flag), 
    size = 0.11) +
  geom_text(
    data = country_labs,
    aes(x = x, y = y, 
        label = country,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = score_labs,
    aes(x = x, y = y, 
        label = score,
        family = "Dusha V5"),
    nudge_y = 0.3, size = 6) +
  geom_text(
    data = goals_labs,
    aes(x = x, y = y, 
        label = scorers,
        family = "Dusha V5"),
    nudge_y = -0.25, size = 4) +
  geom_text(
    data = points_labs,
    aes(x = x, y = y, 
        label = points,
        family = "Dusha V5"),
    size = 5) +
  scale_y_reverse(
    expand = c(0, 0), 
    limits = c(4.8, 0.6),
    breaks = 1:4,
    labels = y_labs) +
  scale_x_continuous(
    position = "top", 
    breaks = 1:4,
    labels = x_labs,
    expand = c(0, 0),
    limits = c(0.6, 5)) +
  labs(
    title = "Group H Table Throughout The Last Matchday",
    subtitle = "Japan vs. Poland & Senegal vs. Colombia",
    caption = "by @R_By_Ryo") +
  theme_minimal() +
  theme(
    text = element_text(family = "Dusha V5", size = 18),
    axis.title = element_blank(),
    legend.position = "none",
    panel.grid = element_blank())

ggsave(groupH, filename = "groupH_table.png")
```


