---
title: "Untitled"
author: "RN7"
date: "June 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


ggjoy plots    minutes goal scored across Group Stages


- webscrape: use SelectorGadget this time...! click on the elements you want to scrape, copy CSS Selector into html_nodes(), pass html_text or html_table and save! 
- reshape: everything in one row of column "value", take regex "^Group" make them new cols, group them up underneath each Group name col 
- tidy: grab minutes text, clean out apostrophe/player name/(o.g.), separate on '+' fill in 0 for non extra time goals then mutate() then sum() ??? 

what COLOR? 

different color scheme for different group?

check out scico , pomographical, hrbrthemes, wes anderson palettes



```{r}
library(rvest)
library(dplyr)

url <- "https://ja.wikipedia.org/wiki/2018_FIFAワールドカップ"

url %>% 
  read_html() %>% 
  html_nodes("tr+ tr span") %>% 
  html_text()


#### actual

url <- "https://en.wikipedia.org/wiki/2018_FIFA_World_Cup"

group_goals <- url %>% 
  read_html() %>% 
  html_nodes("#Group_A , #Group_B , #Group_C , #Group_D , #Group_E , #Group_F , #Group_G , #Group_H,  .plainlist small") %>% 
  html_text() %>% 
  as_tibble()

# write.csv(group_goals, "group_goals.csv", row.names = FALSE)

"#Group_A , #Group_B , #Group_C , #Group_D , #Group_E , #Group_F , #Group_G , #Group_H, .plainlist small"
```



```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)

group_goals <- read.csv("group_goals.csv", stringsAsFactors = FALSE)

group_goals <- group_goals %>% rownames_to_column()

group_name <- group_goals %>% select(value) %>% str_extract_all("Group [A-Z]") %>% as_vector()

goal_length <- group_goals %>% 
  filter(value %in% group_name) %>% 
  mutate(
    rowpos = as.numeric(rowname)) %>% 
  select(-rowname) %>% 
  rownames_to_column() %>% 
  mutate(
    goal_start = rowpos + 1, 
    goal_end = lead(rowpos) - 1,
    goal_end = case_when(
      is.na(goal_end) ~ 130,  # manually set 130 (nrow(group_goals))
      TRUE ~ goal_end
    )) %>% 
  select(-rowpos, -rowname)

1:8 # vector of 1 for each group A-H
group_goals # object to map the slice() through

group_goals %>% 
  slice(goal_length$goal_start[1]:goal_length$goal_end[1]) %>% 
  mutate(groupname = "Group A")

group_goals %>% 
  slice(goal_length$goal_start[2]:goal_length$goal_end[2])

group_goals %>% 
  slice(goal_length$goal_start[3]:goal_length$goal_end[3])

1:8 %>% 
  map2(.x, group_goals, 
       ~ slice(goal_length$goal_end[.x]:goal_length$goal_end[.x]))


goalthing <- NULL


for (i in seq_along(1:8)) {
  
  goalthing[i] <- group_goals %>% 
    slice(goal_length$goal_end[i]:goal_length$goal_end[i])
  
}

group_goals %>% 
  slice()


```

grab rowname pos for each group

slice rows between each group into separate cols




```{r}
library(ggridges)


```























