---
title: "Untitled"
author: "RN7"
date: "December 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r message=FALSE}
pacman::p_load(tidyverse, scales, lubridate, ggrepel, stringi, magick, gapminder,
               glue, extrafont, rvest, ggtextures, cowplot, countrycode, ggimage,
               polite)
# necessary for Roboto Condensed font
loadfonts()
```

# Top goal scorers

```{r}
ac_top_scorers <- data.frame(
  player = c("Ali Daei", "Ali Daei", "Ali Daei",
             "Lee Dong Gook", "Lee Dong Gook",
             "Naohiro Takahara", "Naohiro Takahara",
             "Jassem Al-Houwaidi", "Jassem Al-Houwaidi",
             "Younis Mahmoud", "Younis Mahmoud", "Younis Mahmoud", "Younis Mahmoud"),
  country = c("Iran", "Iran", "Iran",
              "South Korea", "South Korea",
              "Japan", "Japan",
              "Kuwait", "Kuwait",
              "Iraq", "Iraq", "Iraq", "Iraq"),
  tournament = c("1996", "2000", "2004",
                 "2000", "2004",
                 "2000", "2004",
                 "1996", "2000",
                 "2004", "2007", "2011", "2015"),
  goals = as.numeric(c(8, 3, 3,
            6, 4,
            5, 4,
            6, 2,
            1, 4, 1, 2)),
  total_goals = as.numeric(c(14, 14, 14,
            10, 10,
            9, 9,
            8, 8,
            8, 8, 8, 8))
)

# soccer ball images
# https://i.pinimg.com/originals/e7/d7/19/e7d7190f0b5b3abd4f6c17e2c7989ec3.jpg
# https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png
ac_top_scorers <- ac_top_scorers %>% 
  mutate(image = case_when(
    tournament == "2004" ~ "http://football-balls.com/ball_files/2004-asian-cup-adidas-roteiro-official-match-ball.png",
    tournament == "2007" ~ "http://football-balls.com/ball_files/2007-asian-cup-mercurial-veloci-official-match-ball.png",
    tournament == "2011" ~ "http://football-balls.com/ball_files/2011-asian-cup-nike-total-90-tracer-official-match-ball.png",
    tournament == "2015" ~ "http://football-balls.com/ball_files/2015-asian-cup-nike-ordem-2-official-match-ball.png",
    TRUE ~ "https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png")) %>% 
  mutate(country_code = country %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))


ac_top_scorers %>% 
  gather(key = "player", value = "tournament")

ac_top_scorers %>% 
  distinct(player, .keep_all = TRUE)
```


```{r, fig.width=8, fig.height=6}
ac_top_graph <- ac_top_scorers %>% 
  distinct(player, .keep_all = TRUE) %>% 
  ggplot(aes(x = reorder(player, total_goals), y = total_goals,
             image = image)) +
  #ggimage::geom_emoji(aes(image = '26bd'), size = 0.06) +
  geom_isotype_col(img_width = grid::unit(1, "native"), img_height = NULL,
    ncol = NA, nrow = 1, hjust = 0, vjust = 0.5) +
  coord_flip() +
  #geom_flag(y = -1.5, aes(image = country_code), size = 0.1) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                     expand = c(0, 0), 
                     limits = c(0, 15)) +
  #expand_limits(y = -2) +
  ggthemes::theme_solarized() +
  labs(title = "Top Scorers of the Asian Cup!",
       subtitle = "Most goals in a single tournament: 8 (Ali Daei, 1996)",
       y = "Number of Goals", x = NULL) +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        subtitle = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks.y = element_blank())

# scale them differently as flag sizes are different...
pimage <- axis_canvas(ac_top_graph, axis = 'y') + 
  draw_image("https://upload.wikimedia.org/wikipedia/commons/c/ca/Flag_of_Iran.svg", 
             y = 13, scale = 1.5) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/0/09/Flag_of_South_Korea.svg", 
             y = 10, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/en/9/9e/Flag_of_Japan.svg", 
             y = 7, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/f/f6/Flag_of_Iraq.svg", 
             y = 4, scale = 1.6) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/a/aa/Flag_of_Kuwait.svg", 
             y = 1, scale = 1.2)

# insert the image strip into the bar plot and draw  
ggdraw(insert_yaxis_grob(ac_top_graph, pimage, position = "left"))
```


```{r}
theme_void
ggthemes::theme_wsj
ggthemes::theme_solarized
```





# Goals scored per tournament

```{r}
wiki_url <- "https://en.wikipedia.org"
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

cup_links <- read_html(acup_url) %>% 
  html_nodes("br+ i a") %>% 
  html_attr("href") %>% 
  .[-17:-18]


acup_df <- cup_links %>% 
  as_data_frame() %>% 
  mutate(cup = str_remove(value, "\\/wiki\\/") %>% str_replace_all("_", " ")) %>% 
  rename(link = value)



goals_info <- function(x) {
  goal_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Goals scored`) %>% 
    mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
             str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
}

team_num_info <- function(x) {
  team_num_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Teams`) %>% 
    mutate(`Teams` = as.numeric(`Teams`))
}

match_num_info <- function(x) {
  match_num_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    janitor::clean_names() %>% 
    select(matches_played) %>% 
    mutate(matches_played = as.numeric(matches_played))
}


# all together:
goals_data <- acup_df %>% 
  mutate(goals_per_game = map(acup_df$link, goals_info) %>% unlist,
         team_num = map(acup_df$link, team_num_info) %>% unlist,
         match_num = map(acup_df$link, match_num_info) %>% unlist)

```

```{r}
ac_goals_df <- goals_data %>% 
  mutate(label = cup %>% str_extract("[0-9]+") %>% str_replace("..", "'"),
         team_num = case_when(
           is.na(team_num) ~ 16,
           TRUE ~ team_num
         )) %>% 
  arrange(cup) %>% 
  mutate(label = factor(label, label),
         team_num = c(4, 4, 4, 5, 6, 6, 10, 10, 10, 8, 12, 12, 16, 16, 16, 16))
```


```{r}
ac_goals_df %>% 
  ggplot(aes(x = label, y = goals_per_game, group = 1)) +
  geom_line() +
  #geom_point() +
  scale_y_continuous(limits = c(NA, 5.35),
                     breaks = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5)) +
  labs(x = "Tournament (Year)", y = "Goals per Game"#,
       # title = "Goals per Game throughout the Asian Cup.",
       # subtitle = "Odd dip throughout the 80s to early 90s..."
       ) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        #title = element_text(size = 18),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  annotate(geom = "label", x = "'56", y = 5.23, family = "Roboto Condensed",
           color = "black", #fill = "grey",
           label = "Total Number of Games Played:", hjust = 0) +
  annotate(geom = "text", x = "'60", y = 4.9, 
           label = "6", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 1, xend = 3, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'68", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 3.8, xend = 4.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'72", y = 4.9, 
           label = "13", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 4.8, xend = 5.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'76", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 5.8, xend = 6.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'84", y = 4.9, 
           label = "24", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 7, xend = 9, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'92", y = 4.9, 
           label = "16", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 9.8, xend = 10.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 11.5, y = 4.9, 
           label = "26", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 11, xend = 12, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 14.5, y = 4.9, 
           label = "32", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 13, xend = 16, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 9, y = 4, family = "Roboto Condensed",
           label = glue("
                        Incredibly low amount of goals in Group B
                        (15 in 10 Games) and in Knock-Out Stages
                        (4 goals in 4, only one scored in normal time)")) +
  annotate(geom = "segment", x = 9, xend = 9, y = 1.6, yend = 3.6,
           color = "red") +
  ggimage::geom_emoji(aes(image = '26bd'), size = 0.03) 

ggsave(filename = paste0(here::here("Asian Cup 2019"), "/gpg_plot.png"))
plot <- image_read(paste0(here::here("Asian Cup 2019"), "/gpg_plot.png"))
```

## add logo

```{r}
logo_raw <- image_read("https://upload.wikimedia.org/wikipedia/en/a/ad/2019_afc_asian_cup_logo.png")

logo <- logo_raw %>% 
  image_scale("100") %>% 
  image_background("grey", flatten = TRUE) %>% 
  image_border("grey", "600x10") %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "white", size = 30, 
                 location = "+10+50", gravity = "northwest")

final_plot <- image_append(image_scale(c(logo, plot), "500"), stack = TRUE)

logo_proc <- logo_raw %>% image_scale("100")

# create blank canvas
a <- image_blank(width = 6, height = 0.8, color = "white")

# combine with logo and shit it to the left, to the left
b <- image_composite(image_scale(a, "x100"), image_scale(logo_proc, "x60"), 
                     offset = "+500+25")
logo_2 <- b %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "black", size = 18, font = "Roboto Condensed",
                 location = "+63+50", gravity = "northwest")

final2_plot <- image_append(image_scale(c(logo_2, plot), "500"), stack = TRUE)
final2_plot
image_write(final2_plot,
            paste0(here::here("Asian Cup 2019"), "/gpg_plot_final.png"))
```

- annotate number of matches played on top as strip
- fit avg goals per game per each sequence of # of matches >>> kinda like splines
- add AFC logo? top right corner
- put top scorer country as geom_point?
- soccer ball emoji as geom_point?
- patchwork to include top scoring countries + other additional info





```{r}
wiki_url %>% 
  html_session() %>% 
  jump_to("/wiki/2015_AFC_Asian_Cup") %>% 
  html_nodes(".vcalendar") %>% 
  html_table(header = FALSE) %>% 
  flatten_df() %>% 
  spread(key = X1, value = X2) %>% 
  select(`Goals scored`) %>% 
  mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
           str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
```


```{r}
###

one_cup <- "https://en.wikipedia.org/wiki/1968_AFC_Asian_Cup"

copa <- one_cup %>% 
  read_html() %>% 
  html_nodes(".vcalendar") %>% 
  html_table(header = FALSE) %>% 
  flatten_df() %>% 
  spread(key = X1, value = X2) %>% 
  janitor::clean_names() %>% 
  select(goals_scored) %>% 
  mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
           str_extract_all("\\d+\\.*\\d*") %>% as.numeric) # \\(.*)

```








# Asian Cup record

```{r}
# .navigation-not-searchable+ .jquery-tablesorter

acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

session <- bow(acup_url)

acup_winners_raw <- scrape(session) %>% 
  html_nodes("#mw-content-text > div > table:nth-child(30)") %>% 
  html_table() %>% 
  flatten_df()
```

```{r}
acup_winners_clean <- acup_winners_raw %>% 
  janitor::clean_names() %>% 
  slice(1:8) %>% 
  select(-fourth_place, -total_top_four) %>% 
  separate(winners, into = c("first_num", "first_place_year"), sep = " ", extra = "merge") %>% 
  separate(runners_up, into = c("second_num", "second_place_year"), sep = " ", extra = "merge") %>% 
  separate(third_place, into = c("third_num", "third_place_year"), sep = " ", extra = "merge") %>% 
  mutate_all(funs(str_replace_all(., "–", "0"))) %>% 
  mutate_at(vars(contains("num")), funs(as.numeric)) %>% 
  mutate(team = if_else(team == "Israel1", "Israel", team)) %>% 
  gather(key = "key", value = "value", -team, 
         -first_place_year, -second_place_year, -third_place_year) %>% 
  mutate(key = case_when(
           key == "first_num" ~ "Champions",
           key == "second_num" ~ "Runners-up",
           key == "third_num" ~ "Third Place"
         ),
         key = key %>% fct_relevel(c("Champions", "Runners-up", "Third Place"))) %>% 
  # hack-ish solution?
  arrange(key, value) %>% 
  mutate(team = as_factor(team),
         order = row_number(),
         image = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))
```

```{r, fig.width = 8, fig.height = 6}
a <- acup_winners_clean %>% 
  ggplot(aes(value, team, color = key)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("Champions" = "#FFCC33",
                                "Runners-up" = "#999999",
                                "Third Place" = "#CC6600"),
                     guide = FALSE) +
  labs(x = "Number of Occurrence",
       title = "Winners & Losers of the Asian Cup (1956-2015)",
       subtitle = glue("
                       Ordered by number of Asian Cup(s) won.
                       Four-time Champions, Japan, only won their first in 1992!"),
       caption = glue("
                      Note: Israel was expelled by the AFC in 1974 while Australia joined the AFC in 2006.
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  facet_wrap(~key) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 12),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        plot.caption = element_text(hjust = 0, size = 10),
        panel.border = element_rect(fill = NA, colour = "grey20"),
        panel.grid.minor.x = element_blank(),
        strip.text = element_text(size = 16))

ggsave("../Asian Cup 2019/asiancup_winners.png", width = 8, height = 6)

# a +
#   geom_flag(data = acup_winners_clean, 
#             x = -2, aes(image = image), size = 0.15) +
#   expand_limits(x = -2)

# insert_yaxis_grob()

#null_dev_env <- new.env(parent = emptyenv())
# set_null_device("pdf")
# cairo_pdf()
# ggdraw(add_sub(a, label = "Source: Wikipedia\nBy @R_by_Ryo", x = 0.95, size = 8))
# 
# Cairo::Cairo(1000, 750, "test.png", bg = "white")
# last_plot()
# dev.off()
```




# Working hours & Productivity

```{r}
acup_url <- "https://en.wikipedia.org/wiki/2019_AFC_Asian_Cup"

acup_kickoff <- acup_url %>% 
  read_html() %>% 
  html_nodes("time") %>% 
  html_text() %>% 
  as_data_frame()

# time
```

- calculate +90 minutes for entire game duration
- NOT count extra time or stoppage time
- cross-refernce with other local time zones
- count up total number of hours per each spectator country

```{r}

#tz <- "Asia/"
acup_times_df <- acup_kickoff %>% 
  mutate(match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = dmy_hm(time),
         time_ac2 = force_tz(time2, "Asia/Dubai"), # time based in UTC +4
         time_jp = with_tz(time_ac2, tz = "Asia/Tokyo"), # UTC +4 time converted to Japan
         time_jp_end = time_jp + hm("2 0"),
         time_ac = with_tz(time2, tz = "America/New_York")) %>% # UTC +4 time to NYC
  mutate(diff = make_difftime(hour = 2),
         int = as.interval(diff, time_ac2),
         jp_start = ymd_hms("2019-01-05 09:00:00"),
         jp_end = ymd_hms("2019-01-05 12:00:00"),
         jp_work = as.interval(jp_start, jp_end))

acup_times_df$jp_work %within% acup_times_df$int

```

ymd_hms("2011-07-01 09:00:00", tz = "Pacific/Auckland")


# Japan vs. RIVALS

- use Kaggle international results
- results UP TO END OF WORLD CUP
- filter AFC Asian Cup, Friendly, AFC Asian Cup qualification
- filter Asia >>> take out UEFA countries like Kazakhstan, Georgia, Israel, etc.


- https://www.kaggle.com/phjulien/a-journey-through-the-history-of-soccer/

```{r}
federation_files <- Sys.glob("../data/federation_affiliations/*")

df_federations = data.frame(country = NULL, federation = NULL)
for (f in federation_files) {
    federation = basename(f)
    content = read.csv(f, header=FALSE)
    content <- cbind(content,federation=rep(federation, dim(content)[1]))
    df_federations <- rbind(df_federations, content)
}

colnames(df_federations) <- c("country", "federation")

df_federations <- df_federations %>% 
  mutate(country = as.character(country) %>% str_trim(side = "both"))
```

```{r}
results_raw <- read_csv("../data/results.csv")

results_japan_raw <- results_raw %>% 
  filter(home_team == "Japan" | away_team == "Japan") %>% 
  rename(venue_country = country, 
         venue_city = city) %>% 
  mutate(match_num = row_number())

# combine with federation affiliations
results_japan_home <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("home_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(home_federation = federation) #%>% 
  View()

results_japan_away <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("away_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(away_federation = federation) #%>% 
  View()

# combine home-away
results_japan_cleaned <- results_japan_home %>% 
  full_join(results_japan_away)

results_japan_cleaned %>% 
  filter(is.na(home_federation)) %>% 
  pull(home_team) %>% 
  unique()

results_japan_cleaned %>% 
  filter(is.na(away_federation)) %>% 
  pull(away_team) %>% 
  unique()

```



```{r}
results_japan_cleaned <- results_japan_cleaned %>% 
  mutate(
    home_federation = case_when(
      home_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei") ~ "AFC",
      home_team == "USA" ~ "Concacaf",
      home_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ home_federation),
    away_federation = case_when(
      away_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei", "Taiwan") ~ "AFC",
      away_team == "USA" ~ "Concacaf",
      away_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ away_federation
    ))
```

Now that it's nice and cleaned up I can reshape it so that the data is set from Japan's perspective.

```{r}
# reshape to Japan p.o.v.

results_jp_asia <- results_japan_cleaned %>% 
  # filter only for Japan games and AFC opponents
  filter(home_team == "Japan" | away_team == "Japan",
         home_federation == "AFC" & away_federation == "AFC") %>% 
  select(-contains("federation"), -contains("venue"),
         -neutral, -match_num,
         date, home_team, home_score, away_team, away_score, tournament) %>% 
  # reshape columns to Japan vs. opponent
  mutate(
    opponent = case_when(
      away_team != "Japan" ~ away_team,
      home_team != "Japan" ~ home_team),
    home_away = case_when(
      home_team == "Japan" ~ "home",
      away_team == "Japan" ~ "away"),
    japan_goals = case_when(
      home_team == "Japan" ~ home_score,
      away_team == "Japan" ~ away_score),
    opp_goals = case_when(
      home_team != "Japan" ~ home_score,
      away_team != "Japan" ~ away_score)) %>% 
  # results
  mutate(
    result = case_when(
      japan_goals > opp_goals ~ "Win",
      japan_goals < opp_goals ~ "Loss",
      japan_goals == opp_goals ~ "Draw"),
    result = result %>% as_factor() %>% fct_relevel(c("Win", "Draw", "Loss"))) %>% 
  select(-contains("score"), -contains("team"))


#results_jp_asia %>% View()
```



```{r}
results_jp_asia %>% 
  filter(opponent == "Uzbekistan") %>% 
  group_by(result) %>% 
  count()

results_jp_asia %>% 
  filter(opponent == "Turkmenistan")

results_jp_asia %>% 
  filter(opponent == "Oman") %>% 
  knitr::kable()


results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  tally()

results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(japan_goals),
            o_g = sum(opp_goals),
            n = n()) %>% 
  spread(result, n)
```



```{r}
results_jp_asia %>% 
  filter(opponent %in% c("Australia", "Korea Republic", "Iran")) %>% 
  group_by(result, opponent) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(sum(japan_goals)),
            o_g = sum(sum(opp_goals)),
            n = n()) %>% 
  ungroup() %>% 
  spread(result, n) %>% 
  group_by(opponent) %>% 
  mutate(j_g = sum(j_g),
         o_g = sum(o_g),
         Win = sum(Win, na.rm = TRUE),
         Draw = sum(Draw, na.rm = TRUE),
         Loss = sum(Loss, na.rm = TRUE)) %>% 
  distinct()

```

thankfull south korea should be on the otherside of the bracket and we would also only meet Iran in the semifinals

Japan could meet Australia in the Quarters but without Aaron Mooy they're a much weaker side

Japan have unfortunately lost our rising star, Nakajima, to injury but we have replaced him with World Cup hero Takashi Inui.