---
title: "Untitled"
author: "RN7"
date: "January 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Another year, another big soccer/football tournament! This time it's the grand 

## Packages

```{r message=FALSE}
pacman::p_load(tidyverse, scales, lubridate, ggrepel, stringi, magick, gapminder,
               glue, extrafont, rvest, ggtextures, cowplot, countrycode, ggimage,
               polite)
# Roboto Condensed font (from hrbrmstrthemes or just Google it)
loadfonts()
```


## Top Goalscorers of the Asian Cup

```{r}
topg_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup_records_and_statistics"

session <- bow(topg_url)

ac_top_scorers <- scrape(session) %>%
  html_nodes("table.wikitable:nth-child(29)") %>% 
  html_table() %>% 
  flatten_df() %>% 
  select(-Ref.) %>% 
  set_names(c("total_goals", "player", "country"))
```

For brevity, let's only take a look at the top 5 goal scorers. I'll also `mutate()` in a nice image of a soccer ball for the points on the plot.

```{r}
ac_top_scorers <- ac_top_scorers %>% 
  head(5) %>% 
  mutate(image = "https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png")
```

Now it's ready to plot! Slightly different to your standard bar graph here due to using the `geom_isotype_col()` function from `ggtextures` to create a bar of soccer ball images. Compared to other functions in ggtextures, geom_isotype_col() allows each image to correspond to the value of the variable you are plotting, in this case 1 ball = 1 goal!

```{r top goal scorers plot, fig.width=8, fig.height=6}
ac_top_graph <- ac_top_scorers %>% 
  ggplot(aes(x = reorder(player, total_goals), y = total_goals,
             image = image)) +
  geom_isotype_col(img_width = grid::unit(1, "native"), img_height = NULL,
    ncol = NA, nrow = 1, hjust = 0, vjust = 0.5) +
  coord_flip() +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                     expand = c(0, 0), 
                     limits = c(0, 15)) +
  ggthemes::theme_solarized() +
  labs(title = "Top Scorers of the Asian Cup",
       subtitle = "Most goals in a single tournament: 8 (Ali Daei, 1996)",
       y = "Number of Goals", x = NULL,
       caption = glue("
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  theme(text = element_text(family = "Roboto Condensed"),
        plot.title = element_text(size = 22),
        plot.subtitle = element_text(size = 14),
        axis.text = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.line.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks.y = element_blank())

ac_top_graph
```

OK, not bad. However, wouldn't it be nice to add a bit more information for context? Specifically, which country these players came from. So let's add some flags along the y-axis!

There are lots of different ways to do this (like `geom_flag()` from `ggimage` package) but I ended up doing it the "cowplot" way. I had to tweak the scales a bit as the flags came in different sizes.

Finally, you insert the image strip into the bar plot and combine all the parts together with `ggdraw()`!

```{r draw_image, fig.width=8, fig.height=6}
axis_image <- axis_canvas(ac_top_graph, axis = 'y') + 
  draw_image("https://upload.wikimedia.org/wikipedia/commons/c/ca/Flag_of_Iran.svg", 
             y = 13, scale = 1.5) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/0/09/Flag_of_South_Korea.svg", 
             y = 10, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/en/9/9e/Flag_of_Japan.svg", 
             y = 7, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/f/f6/Flag_of_Iraq.svg", 
             y = 4, scale = 1.6) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/a/aa/Flag_of_Kuwait.svg", 
             y = 1, scale = 1.2)

ggdraw(insert_yaxis_grob(ac_top_graph, axis_image, position = "left"))
```

Ideally I wanted the soccer balls to be the official balls from the tournament that the player scored in. However, I couldn't find a nice emoji-fied/icon-ized version and there was also the small problem in that there was no "official" Asian Cup ball until the 2007 tournament! 


## Winners of the Asian Cup

```{r}
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

# responsible web-scraping ftw!
session <- bow(acup_url)

acup_winners_raw <- scrape(session) %>% 
  html_nodes("#mw-content-text > div > table:nth-child(30)") %>% 
  html_table() %>% 
  flatten_df()
```


```{r}
# clean
acup_winners_clean <- acup_winners_raw %>% 
  janitor::clean_names() %>% 
  slice(1:8) %>% 
  select(-fourth_place, -total_top_four) %>% 
  separate(winners, into = c("first_num", "first_place_year"), sep = " ", extra = "merge") %>% 
  separate(runners_up, into = c("second_num", "second_place_year"), sep = " ", extra = "merge") %>% 
  separate(third_place, into = c("third_num", "third_place_year"), sep = " ", extra = "merge") %>% 
  mutate_all(funs(str_replace_all(., "–", "0"))) %>% 
  mutate_at(vars(contains("num")), funs(as.numeric)) %>% 
  mutate(team = if_else(team == "Israel1", "Israel", team)) %>% 
  gather(key = "key", value = "value", -team, 
         -first_place_year, -second_place_year, -third_place_year) %>% 
  mutate(key = case_when(
    key == "first_num" ~ "Champions",
    key == "second_num" ~ "Runners-up",
    key == "third_num" ~ "Third Place"
  ),
  key = key %>% fct_relevel(c("Champions", "Runners-up", "Third Place"))) %>% 
  # hack-ish solution?
  arrange(key, value) %>% 
  mutate(team = as_factor(team),
         order = row_number())
```


```{r}
# PLOT
acup_winners_clean %>% 
  ggplot(aes(value, team, color = key)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("Champions" = "#FFCC33",
                                "Runners-up" = "#999999",
                                "Third Place" = "#CC6600"),
                     guide = FALSE) +
  labs(x = "Number of Occurrence",
       title = "Winners & Losers of the Asian Cup!",
       subtitle = glue("
                       Ordered by number of Asian Cup(s) won.
                       Four-time Champions, Japan, only won their first in 1992!"),
       caption = glue("
                      Note: Israel was expelled by the AFC in 1974 while Australia joined the AFC in 2006.
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  facet_wrap(~key) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 12),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        plot.caption = element_text(hjust = 0, size = 10),
        panel.border = element_rect(fill = NA, colour = "grey20"),
        panel.grid.minor.x = element_blank(),
        strip.text = element_text(size = 16)) 
```


## Goals per Game

one new thing i learned very recently, using magrittr aliases! 

![](https://twitter.com/Emil_Hvitfeldt/status/1081080919073542144) pic of Emil Hvitfeldt tweet

usualyl for webscraping i always wind up having to use the `.[]` or `.[[]]` but now I can just use `extract()` or `extract2()` respectively to do the same thing!

```{r GPG base links}
wiki_url <- "https://en.wikipedia.org"
session <- bow(wiki_url)
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"
session_cup <- bow(acup_url)

cup_links <- scrape(session_cup) %>% 
  html_nodes("br+ i a") %>% 
  html_attr("href") %>% 
  magrittr::extract(-17:-18)

acup_df <- cup_links %>% 
  as_data_frame() %>% 
  mutate(cup = str_remove(value, "\\/wiki\\/") %>% str_replace_all("_", " ")) %>% 
  rename(link = value)
```



I could have consolidate the three separate functions into one but some of the scraping and cleaning needed a bit more work then the others.

```{r goal info functions}
goals_info <- function(x) {
  goal_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Goals scored`) %>% 
    mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
             str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
}

team_num_info <- function(x) {
  team_num_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Teams`) %>% 
    mutate(`Teams` = as.numeric(`Teams`))
}

match_num_info <- function(x) {
  match_num_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    janitor::clean_names() %>% 
    select(matches_played) %>% 
    mutate(matches_played = as.numeric(matches_played))
}

# all together:
goals_data <- acup_df %>% 
  mutate(goals_per_game = map(acup_df$link, goals_info) %>% unlist,
         team_num = map(acup_df$link, team_num_info) %>% unlist,
         match_num = map(acup_df$link, match_num_info) %>% unlist)

```

clean up and add in number of teams that participated in each tournament

```{r clean up}
ac_goals_df <- goals_data %>% 
  mutate(label = cup %>% str_extract("[0-9]+") %>% str_replace("..", "'"),
         team_num = case_when(
           is.na(team_num) ~ 16,
           TRUE ~ team_num
         )) %>% 
  arrange(cup) %>% 
  mutate(label = factor(label, label),
         team_num = c(4, 4, 4, 5, 6, 6, 10, 10, 10, 8, 12, 12, 16, 16, 16, 16))
```

just your regular line graph but with LOTS of `annotate()` code! This part is really just trial-and-error until you feel you got it juuust right.


```{r}
plot <- ac_goals_df %>% 
  ggplot(aes(x = label, y = goals_per_game, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 5.35),
                     breaks = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5)) +
  labs(x = "Tournament (Year)", y = "Goals per Game") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        #title = element_text(size = 18),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  annotate(geom = "label", x = "'56", y = 5.23, family = "Roboto Condensed",
           color = "black", #fill = "grey",
           label = "Total Number of Games Played:", hjust = 0) +
  annotate(geom = "text", x = "'60", y = 4.9, 
           label = "6", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 1, xend = 3, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'68", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 3.8, xend = 4.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'72", y = 4.9, 
           label = "13", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 4.8, xend = 5.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'76", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 5.8, xend = 6.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'84", y = 4.9, 
           label = "24", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 7, xend = 9, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'92", y = 4.9, 
           label = "16", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 9.8, xend = 10.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 11.5, y = 4.9, 
           label = "26", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 11, xend = 12, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 14.5, y = 4.9, 
           label = "32", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 13, xend = 16, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 9, y = 4, family = "Roboto Condensed",
           label = glue("
                        Incredibly low amount of goals in Group B
                        (15 in 10 Games) and in Knock-Out Stages
                        (4 goals in 4, only one scored in normal time)")) +
  annotate(geom = "segment", x = 9, xend = 9, y = 1.6, yend = 3.6,
           color = "red") +
  ggimage::geom_emoji(aes(image = '26bd'), size = 0.03) 

plot
```

add the Asian Cup logo!


dove ack into my bookmark folders to find []() blog post by daniel hadley

this wasn't my first time using magick apckage but back then it was for animation processing rather than image editing.

```{r}
logo_raw <- image_read("https://upload.wikimedia.org/wikipedia/en/a/ad/2019_afc_asian_cup_logo.png")

logo_proc <- logo_raw %>% image_scale("100")

# create blank canvas
a <- image_blank(width = 6, height = 0.8, color = "white")
# combine with logo image and shift logo to the right
b <- image_composite(image_scale(a, "x100"), image_scale(logo_proc, "x60"), 
                     offset = "+500+25")
# add in the title text
logo_header <- b %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "black", size = 18, font = "Roboto Condensed",
                 location = "+63+50", gravity = "northwest")

# combine it all together!
final2_plot <- image_append(image_scale(c(logo_header, plot), "500"), stack = TRUE)
final2_plot
image_write(final2_plot,
            paste0(here::here("Asian Cup 2019"), "/gpg_plot_final.png"))
```

all in all it took a while to tweak the positions of the text and logo image but for my first try it worked well. also compared to daniel hadley's example i needed to have the logo on the right corner so i had to find an alternative way of creating a blank canvas and the placing everything on top of that 





## Japan's record vs. Group D opponents