---
title: "Untitled"
author: "RN7"
date: "January 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Another year, another big soccer/football tournament! This time it's the top international competition in Asia, the Asian Cup hosted in the U.A.E. 

I'll be covering (responsible) web-scraping, data wrangling (tidyverse ftw!), and of course, data visualization with `ggplot2`.

Let's get started!

## Packages

```{r message=FALSE}
pacman::p_load(tidyverse, scales, lubridate, ggrepel, stringi, magick, 
               glue, extrafont, rvest, ggtextures, cowplot, ggimage, polite)
# Roboto Condensed font (from hrbrmstrthemes or just Google it)
loadfonts()
```


## Top Goalscorers of the Asian Cup

When you talk about football the most important thing is goals. Goals, goals, and lots of goals. So, the first thing I looked at was who were the top goalscorers in the history of the Asian Cup?

Here I use the [polite](https://github.com/dmi3kno/polite) package to take a look at the `robots.txt` for the web page and see if it is OK to  web scrape. It really shouldn't be an issue for Wikipedia but it's good to make things like this a habit! 

First you pass the URL to the `bow()` function, check that you are indeed allowed to scrape, then use `scrape()` to retrieve data, and the rest is the usual `rvest` web-scraping workflow.

```{r}
topg_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup_records_and_statistics"

session <- bow(topg_url)

ac_top_scorers <- scrape(session) %>%
  html_nodes("table.wikitable:nth-child(29)") %>% 
  html_table() %>% 
  flatten_df() %>% 
  select(-Ref.) %>% 
  set_names(c("total_goals", "player", "country"))
```

For brevity, let's only take a look at the top 5 goal scorers. I'll also `mutate()` in a nice image of a soccer ball for the data points on the plot.

```{r}
ac_top_scorers <- ac_top_scorers %>% 
  head(5) %>% 
  mutate(image = "https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png")
```

Now it's ready! Slightly different to your standard bar graph here due to using the `geom_isotype_col()` function from `ggtextures` to create a bar of soccer ball images. Compared to other functions in ggtextures, `geom_isotype_col()` allows each image to correspond to the value of the variable you are plotting, in this case 1 ball = 1 goal!

```{r top goal scorers plot, fig.width=8, fig.height=6}
ac_top_graph <- ac_top_scorers %>% 
  ggplot(aes(x = reorder(player, total_goals), y = total_goals,
             image = image)) +
  geom_isotype_col(img_width = grid::unit(1, "native"), img_height = NULL,
    ncol = NA, nrow = 1, hjust = 0, vjust = 0.5) +
  coord_flip() +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                     expand = c(0, 0), 
                     limits = c(0, 15)) +
  ggthemes::theme_solarized() +
  labs(title = "Top Scorers of the Asian Cup",
       subtitle = "Most goals in a single tournament: 8 (Ali Daei, 1996)",
       y = "Number of Goals", x = NULL,
       caption = glue("
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  theme(text = element_text(family = "Roboto Condensed"),
        plot.title = element_text(size = 22),
        plot.subtitle = element_text(size = 14),
        axis.text = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.line.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks.y = element_blank())

ac_top_graph
```

OK, not bad. However, wouldn't it be nice to add a bit more information for context? Specifically, which country these players came from. So let's add some flags along the y-axis!

There are lots of different ways to do this (like `geom_flag()` from `ggimage` package) but I ended up doing it the "cowplot" way. I had to tweak the scales a bit as the flags came in different sizes.

Finally, you insert the image strip into the bar plot and combine all the parts together with `ggdraw()`!

```{r draw_image, fig.width=8, fig.height=6}
axis_image <- axis_canvas(ac_top_graph, axis = 'y') + 
  draw_image("https://upload.wikimedia.org/wikipedia/commons/c/ca/Flag_of_Iran.svg", 
             y = 13, scale = 1.5) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/0/09/Flag_of_South_Korea.svg", 
             y = 10, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/en/9/9e/Flag_of_Japan.svg", 
             y = 7, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/f/f6/Flag_of_Iraq.svg", 
             y = 4, scale = 1.6) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/a/aa/Flag_of_Kuwait.svg", 
             y = 1, scale = 1.2)

ggdraw(insert_yaxis_grob(ac_top_graph, axis_image, position = "left"))
```

Ideally I wanted the soccer balls to be the official balls from the tournament that the player scored in. However, I couldn't find a nice emoji-fied/icon-ized version and there was also the "small" problem in that there was no "official" Asian Cup ball until the 2007 tournament! 

You can take a look at the official Asian Cup balls [here]().


## Winners of the Asian Cup

We saw that the top goal scorers came from Iran, South Korea, Japan, Iraq, and Kuwait but did their goal scoring exploits lead their nations to glory? Let's find out!

I really like using `flatten_df()` after `html_table()` as I don't have to use the awkward looking `.[[1]]` within my piped workflow.

```{r}
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

session <- bow(acup_url)

acup_winners_raw <- scrape(session) %>% 
  html_nodes("table:nth-child(31)") %>% 
  html_table() %>% 
  flatten_df()
```

Now I can use the `clean_names()` function to quickly clean up my names (mainly when I can't be bothered to `set_names()` them myself...).

The next steps are splitting up the number of times a team placed between 1st and 3rd and the year that occured with `separate()`. 

The variants of `mutate()` are then used to tidy the string columns of the data into numeric.

I use `gather()` so each team will have a row for each of the rank positions (1st-3rd). 

Finally I arrange the data in a way that the facets will be ordered in the way that I want.

```{r}
# clean
acup_winners_clean <- acup_winners_raw %>% 
  janitor::clean_names() %>% 
  slice(1:8) %>% 
  select(-fourth_place, -total_top_four) %>% 
  separate(winners, into = c("Champions", "first_place_year"), sep = " ", extra = "merge") %>% 
  separate(runners_up, into = c("Runners-up", "second_place_year"), sep = " ", extra = "merge") %>% 
  separate(third_place, into = c("Third Place", "third_place_year"), sep = " ", extra = "merge") %>% 
  mutate_all(funs(str_replace_all(., "–", "0"))) %>% 
  mutate_at(vars(contains("num")), funs(as.numeric)) %>% 
  mutate(team = if_else(team == "Israel1", "Israel", team)) %>% 
  gather(key = "key", value = "value", -team, 
         -first_place_year, -second_place_year, -third_place_year) %>% 
  mutate(key = key %>% 
           fct_relevel(c("Champions", "Runners-up", "Third Place"))) %>% 
  arrange(key, value) %>% 
  mutate(team = as_factor(team),
         order = row_number())

acup_winners_clean %>% knitr::kable()
```

I plot using facets on the "key" variable (containing the rank data) so that we can see how many times placed as Champions to Third Place. I also use the `glue()` function here to format the multi-line captions and titles in a neat way.

```{r}
# PLOT
acup_winners_clean %>% 
  ggplot(aes(value, team, color = key)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("Champions" = "#FFCC33",
                                "Runners-up" = "#999999",
                                "Third Place" = "#CC6600"),
                     guide = FALSE) +
  labs(x = "Number of Occurrence",
       title = "Winners & Losers of the Asian Cup!",
       subtitle = glue("
                       Ordered by number of Asian Cup(s) won.
                       Four-time Champions, Japan, only won their first in 1992!"),
       caption = glue("
                      Note: Israel was expelled by the AFC in 1974 while Australia joined the AFC in 2006.
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  facet_wrap(~key) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 12),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        plot.caption = element_text(hjust = 0, size = 10),
        panel.border = element_rect(fill = NA, colour = "grey20"),
        panel.grid.minor.x = element_blank(),
        strip.text = element_text(size = 16)) 
```

It would have been nice to include the respective years that these teams ranked 

## Goals per Game

For this graph I wanted to see whether there were 



one new thing i learned very recently, using magrittr aliases! 

![](https://twitter.com/Emil_Hvitfeldt/status/1081080919073542144) pic of Emil Hvitfeldt tweet

usualyl for webscraping i always wind up having to use the `.[x]` or `.[[x]]` but now I can just use `extract()` or `extract2()` respectively to do the same thing!

```{r GPG base links}
wiki_url <- "https://en.wikipedia.org"
session <- bow(wiki_url)
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"
session_cup <- bow(acup_url)

cup_links <- scrape(session_cup) %>% 
  html_nodes("br+ i a") %>% 
  html_attr("href") %>% 
  magrittr::extract(-17:-18)

acup_df <- cup_links %>% 
  as_data_frame() %>% 
  mutate(cup = str_remove(value, "\\/wiki\\/") %>% str_replace_all("_", " ")) %>% 
  rename(link = value)
```

The cool thing I found while trying to scrape this data was the `jump_to()` function that allows you to navigate to a new URL. This makes `map()`-ing over multiple URL links from a base URL very easy! Here, the base URL is the AFC Asian Cup Wikipedia page and the function iterates over each of the links to the URL of the respective tournament pages. Another way that I could've done this was to `map()` over the different dates of the tournaments as the Wikipedia page of each edition of the Asian Cup only differend in the "year" appended at the beginning of the URL. I could have consolidated the three separate functions into one but some needed a bit more work than the others.

```{r goal info functions}
goals_info <- function(x) {
  goal_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Goals scored`) %>% 
    mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
             str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
}

team_num_info <- function(x) {
  team_num_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Teams`) %>% 
    mutate(`Teams` = as.numeric(`Teams`))
}

match_num_info <- function(x) {
  match_num_info <- scrape(session) %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    janitor::clean_names() %>% 
    select(matches_played) %>% 
    mutate(matches_played = as.numeric(matches_played))
}

# all together:
goals_data <- acup_df %>% 
  mutate(goals_per_game = map(acup_df$link, goals_info) %>% unlist,
         team_num = map(acup_df$link, team_num_info) %>% unlist,
         match_num = map(acup_df$link, match_num_info) %>% unlist)

```

No to clean it up a bit and add in the number of teams that participated in each tournament.

```{r clean up}
ac_goals_df <- goals_data %>% 
  mutate(label = cup %>% str_extract("[0-9]+") %>% str_replace("..", "'"),
         team_num = case_when(
           is.na(team_num) ~ 16,
           TRUE ~ team_num
         )) %>% 
  arrange(cup) %>% 
  mutate(label = factor(label, label),
         team_num = c(4, 4, 4, 5, 6, 6, 10, 10, 10, 8, 12, 12, 16, 16, 16, 16))
```

Now we make a line graph but with LOTS of `annotate()` code to add in comments, labels, and segments for the label. At the end I use `geom_emoji()` to add a soccer ball to the plot for each of the data points.

```{r}
plot <- ac_goals_df %>% 
  ggplot(aes(x = label, y = goals_per_game, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 5.35),
                     breaks = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5)) +
  labs(x = "Tournament (Year)", y = "Goals per Game") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        #title = element_text(size = 18),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  annotate(geom = "label", x = "'56", y = 5.23, family = "Roboto Condensed",
           color = "black", #fill = "grey",
           label = "Total Number of Games Played:", hjust = 0) +
  annotate(geom = "text", x = "'60", y = 4.9, 
           label = "6", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 1, xend = 3, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'68", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 3.8, xend = 4.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'72", y = 4.9, 
           label = "13", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 4.8, xend = 5.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'76", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 5.8, xend = 6.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'84", y = 4.9, 
           label = "24", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 7, xend = 9, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'92", y = 4.9, 
           label = "16", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 9.8, xend = 10.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 11.5, y = 4.9, 
           label = "26", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 11, xend = 12, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 14.5, y = 4.9, 
           label = "32", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 13, xend = 16, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 9, y = 4, family = "Roboto Condensed",
           label = glue("
                        Incredibly low amount of goals in Group B
                        (15 in 10 Games) and in Knock-Out Stages
                        (4 goals in 4, only one scored in normal time)")) +
  annotate(geom = "segment", x = 9, xend = 9, y = 1.6, yend = 3.6,
           color = "red") +
  ggimage::geom_emoji(aes(image = '26bd'), size = 0.03) 

plot
```

However, I'm not finished yet! I wanted to try to make this look a bit more "official" so I attempted to add the Asian Cup logo on the top right corner. There are probably alternative ways to how I did it below, especially by using grobs, but I was reminded of [this]() blog post by Daniel Hadley who used the `magick` package to add a footer with a logo onto a ggplot object. I've used magick before for animations but this was a good chance to try it out for image editing.

```{r}
logo_raw <- image_read("https://upload.wikimedia.org/wikipedia/en/a/ad/2019_afc_asian_cup_logo.png")

logo_proc <- logo_raw %>% image_scale("100")

# create blank canvas
a <- image_blank(width = 6, height = 0.8, color = "white")
# combine with logo image and shift logo to the right
b <- image_composite(image_scale(a, "x100"), image_scale(logo_proc, "x60"), 
                     offset = "+500+25")
# add in the title text
logo_header <- b %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "black", size = 18, font = "Roboto Condensed",
                 location = "+63+50", gravity = "northwest")

# combine it all together!
final2_plot <- image_append(image_scale(c(logo_header, plot), "500"), stack = TRUE)
final2_plot
image_write(final2_plot,
            paste0(here::here("Asian Cup 2019"), "/gpg_plot_final.png"))
```

all in all it took a while to tweak the positions of the text and logo image but for my first try it worked well. also compared to daniel hadley's example i needed to have the logo on the right corner so i had to find an alternative way of creating a blank canvas with `image_blank()` and the placing everything on top of that with `image_composite()` and `image_append()`

Ultimately, I couldn't find much information on why those tournaments in the 80s in particular were such low scoring affairs. I wasn't alive to watch those games on TV nor could I have any illuminating articles or blog posts on the style of Asian football back in the 80s...This was also before Japan really got into soccer so there wasn't anything I could find in Japanese either.


## Japan's record vs. Group D opponents and rivals

Japan is the most successful team in the competition with 4 championships but who are their opponents in the group stages and how have they fared against them

In the meanwhile we can also check their reocrds against long-time continental rivals such as Iran, South Korea, Saudi Arabia and more recently, Australia.


- use Kaggle international results
- results UP TO END OF WORLD CUP
- filter AFC Asian Cup, Friendly, AFC Asian Cup qualification
- filter Asia >>> take out UEFA countries like Kazakhstan, Georgia, Israel, etc.


- https://www.kaggle.com/phjulien/a-journey-through-the-history-of-soccer/

```{r}
federation_files <- Sys.glob("../data/federation_affiliations/*")

df_federations = data.frame(country = NULL, federation = NULL)
for (f in federation_files) {
    federation = basename(f)
    content = read.csv(f, header=FALSE)
    content <- cbind(content,federation=rep(federation, dim(content)[1]))
    df_federations <- rbind(df_federations, content)
}

colnames(df_federations) <- c("country", "federation")

df_federations <- df_federations %>% 
  mutate(country = as.character(country) %>% str_trim(side = "both"))
```

Now to load the results data and then join it with the affiliations data created by PH Julien.

```{r}
results_raw <- read_csv("../data/results.csv")

results_japan_raw <- results_raw %>% 
  filter(home_team == "Japan" | away_team == "Japan") %>% 
  rename(venue_country = country, 
         venue_city = city) %>% 
  mutate(match_num = row_number())

# combine with federation affiliations
results_japan_home <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("home_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(home_federation = federation) 

results_japan_away <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("away_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(away_federation = federation)

# combine home-away
results_japan_cleaned <- results_japan_home %>% 
  full_join(results_japan_away)
```

Next I need to edit some of the continents for teams that didn't have a match in the federation afiliation data set, for example, "South Korea" is "Korea Republic" in the Kaggle data set.

```{r}
results_japan_cleaned <- results_japan_cleaned %>% 
  mutate(
    home_federation = case_when(
      home_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei") ~ "AFC",
      home_team == "USA" ~ "Concacaf",
      home_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ home_federation),
    away_federation = case_when(
      away_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei", "Taiwan") ~ "AFC",
      away_team == "USA" ~ "Concacaf",
      away_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ away_federation
    ))
```

Now that it's nice and cleaned up I can reshape it so that the data is set from Japan's perspective.

```{r}
results_jp_asia <- results_japan_cleaned %>% 
  # filter only for Japan games and AFC opponents
  filter(home_team == "Japan" | away_team == "Japan",
         home_federation == "AFC" & away_federation == "AFC") %>% 
  select(-contains("federation"), -contains("venue"),
         -neutral, -match_num,
         date, home_team, home_score, away_team, away_score, tournament) %>% 
  # reshape columns to Japan vs. opponent
  mutate(
    opponent = case_when(
      away_team != "Japan" ~ away_team,
      home_team != "Japan" ~ home_team),
    home_away = case_when(
      home_team == "Japan" ~ "home",
      away_team == "Japan" ~ "away"),
    japan_goals = case_when(
      home_team == "Japan" ~ home_score,
      away_team == "Japan" ~ away_score),
    opp_goals = case_when(
      home_team != "Japan" ~ home_score,
      away_team != "Japan" ~ away_score)) %>% 
  # label results from Japan's perspective
  mutate(
    result = case_when(
      japan_goals > opp_goals ~ "Win",
      japan_goals < opp_goals ~ "Loss",
      japan_goals == opp_goals ~ "Draw"),
    result = result %>% as_factor() %>% fct_relevel(c("Win", "Draw", "Loss"))) %>% 
  select(-contains("score"), -contains("team"))
```

With all that done we can take a look at how Japan have done against certain opponents by using `filter()`.

```{r}
results_jp_asia %>% 
  filter(opponent == "Uzbekistan") %>% 
  group_by(result) %>% 
  count()

results_jp_asia %>% 
  filter(opponent == "Turkmenistan")

results_jp_asia %>% 
  filter(opponent == "Oman") %>% 
  knitr::kable()


results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  tally()

results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(japan_goals),
            o_g = sum(opp_goals),
            n = n()) %>% 
  spread(result, n)
```

I can create a function that'll filter for any opponents I might want to take a look at 

```{r}
japan_versus <- function() {
  
}
```



```{r}
results_jp_asia %>% 
  filter(opponent %in% c("Australia", "Korea Republic", "Iran")) %>% 
  group_by(result, opponent) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(japan_goals),
            o_g = sum(opp_goals),
            n = n()) %>% 
  ungroup() %>% 
  spread(result, n) %>% 
  group_by(opponent) %>% 
  summarize(Win = sum(Win, na.rm = TRUE),
         Draw = sum(Draw, na.rm = TRUE),
         Loss = sum(Loss, na.rm = TRUE),
         j_g = sum(j_g),
         o_g = sum(o_g))
```

I'm going to use this opportunity to try out the new `gt` package. 

```{r}

```







# Conclusion

Japan 

South Korea and Iran

thankfull south korea should be on the other side of the bracket and we would also only meet Iran in the semifinals (provided both teams finish top of their respective groups)

Japan could meet Australia in the Quarters but without Aaron Mooy they're a much weaker side as shown in their abject loss to Jordan in their opening match.

even with losing new star Nakajima, the fact that we can replace him with a player of the calibre of Takashi Inui shows how much Japanese football has progressed these past 25 years

it's a changing of the guard for Japan but we've got quality players in Europe as well as some depth too with more young Japanese players headed to Europe from a young age

this tournament should be a first stepping stone for this new generation of players to make a big impact for the next world cup in 2022 so keep your eye out for this bunch of players!